Using simulation to optimize the sampling design of fisheries-independent trawl surveys

### 2019-02-06 analysis/paper/sim_survey_paper.Rmd
Add divergent dot plot and error surface plot to paper (next step: fix docx template for code block and increase font of surface plot)

>>>>

The relative performance of the surveys tested can be compared using `plot_survey_rank` and `plot_error_surface`. The `plot_survey_rank` function produces a divergent dot plot of the results which ranks the surveys by RMSE. Using the `wich_strat` argument, the plot can be focused on total, length or age based stratified results. The `plot_error_surface` focuses solely on the age based stratified results by plotting a surface of RMSE (z-axis) by set (drop down selection), length (y-axis) and age (z-axis) sampling effort. The sampling effort axes can be rule or sample size based (`plot_by = "rule"` or `plot_by = "samples"`, respectively). See figures \@ref(fig:rank) and \@ref(fig:rmse-surface) for examples of the output from the code below.

plot_survey_rank(tests, which_strat = "length")
plot_error_surface(tests, plot_by = "rule")

sim <- tests
sim$surveys <- sim$surveys[sim$surveys$set_den %in% c("0.01", "0.002", "0.0005")]

p <- plot_survey_rank(sim, which_strat = "length")
export_plot(p, file = "analysis/paper/figures/plot_survey_rank.png", width = 450, height = 400)

totals <- sim$samp_totals[, list(n_sets = mean(n_sets), n_caught = mean(n_caught),
                                 n_measured = mean(n_measured), n_aged = mean(n_aged)),
                          by = "survey"]
errors <- merge(sim$surveys, sim$age_strat_error_stats, by = "survey")
d <- merge(errors, totals, by = "survey")

split_d <- split(d, d$set_den)
x <- sort(unique(d$ages_cap))
y <- sort(unique(d$lengths_cap))

scene <- list(
  xaxis = list(title = "Ages cap"),
  yaxis = list(title = "Lengths cap"),
  zaxis = list(title = "RMSE"),
  camera = list(eye = list(x = 1.5, y = 1.5, z = 1.5))
)

xshift <- c(-30, 0, 30)
p_list <- lapply(seq_along(split_d), function(i) {
  scene <- paste0("scene", i)
  z <- stats::xtabs(RMSE ~ ages_cap + lengths_cap, data = split_d[[i]], subset = NULL)
  plot_ly(x = x, y = y, scene = scene) %>% add_surface(z = t(z), showscale = FALSE) %>% 
    add_labels(x = 0.5, y = 1, text = paste("D<sub>sets</sub> =", names(split_d[i])), 
               yshift = -20, xshift = xshift[i])
})

p <- subplot(p_list) %>%  
  layout(scene = c(list(domain = list(x = c(0, 1/3), y = c(0, 1))), scene),
         scene2 = c(list(domain = list(x = c(1/3, 2/3), y = c(0, 1))), scene),
         scene3 = c(list(domain = list(x = c(2/3, 1), y = c(0, 1))), scene),
         autosize = FALSE, margin = list(t = 0, l = 10, r = 10, b = 10))

export_plot(p, file = "analysis/paper/figures/plot_error_surface.png", width = 1250, height = 400)

```{r rank, fig.cap = "- Divergent dot plot of the percision and accuracy (RMSE) of length based stratified estimates of abundance, and total sampling effort (number of sets [$N_{sets}$] and length measurements [$N_{measured}$]), under various sampling protocol (set density [$D_{sets}$] and maximum number of lengths measured per set [$M_{lengths}$])."}

knitr::include_graphics("figures/plot_survey_rank.png")

```{r rmse-surface, fig.cap = "- Surface plots of RMSE from an array of surveys with different sampling protocol. Panels represent surveys with different set densities ($D_{sets}$), x-axes represent the maximum sampling effort of lengths per set ($M_{lengths}$), and y-axes represent the maximum number of ages to collect per length group (M_{ages}). This plot is a facet of plots produced by `plot_error_surface` when supplied results from `test_surveys`. Note that the z-axes scales are different across the facets."}

knitr::include_graphics("figures/plot_error_surface.png")
